### 2013-09-18 chi2014/method.tex

The brainstorming task was presented in a standard web-based form that included an introduction, the specific brainstorming problem, a series of fields for entering the individual responses, and a larger text area where workers could enter additional ideas (TODO: Figure X).

The introduction Osborne's four rules of brainstorming \cite{osborn_applied_1957}, adapted to this context:

@@

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the risk their responses and idea generation processes evolved over time, making it difficult to compare their responses in the second HIT with responses from others who are performing the same HIT without any previous exposure to the problem. Accordingly, we retain only the first HIT submitted by the same worker.

After removing these data, we are left with 146 distinct participants for a total of 146 HITs, yielding 3007 responses. A breakdown of responses across conditions is given in table TODO: TAB.

\begin{tabular}[h!]{r | l l l l l l }
& 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
HITs completed & 59 & 49 & 23 & 10 & 10 & 10 \\
HITs completed (no repeats) & 57 & 39 & 21 & 9 & 10 & 10 \\
solutions (no repeats) & 283 & 372 & 413 & 450 & 635 & 855 \\
\end{tabular}

@@

\subsubsection{Clustering: Terminology}
An \emph{instance} is a single solution by a single participant to a brainstorming question. Most concretely, it is the text entered into a single field in the web form. For example, figure~\ref{fig:sample_instances} provides an example of four \emph{instances} from workers.

\begin{figure}[!h]
    \begin{enumerate}
        \item "Storage Container"
        \item "Small Storage Box"
        \item "Coin Storage"
        \item "Travel Jewelry Case"
    \end{enumerate}
    \label{sample_instances}
\end{figure}

@@

In a category tree, ideas act as nodes. Each idea may optionally have a single parent idea, and zero or more child ideas. If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B. An example category tree for the instances in Figure FIG is given in Figure FIG.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{example_instances}
\end{figure}

>>>>

The brainstorming task was presented in a standard web-based form that included an introduction, the specific brainstorming problem, a series of fields for entering the individual responses, and a larger text area where workers could enter additional ideas (Figure~\ref{fig:sample_task}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{sample_task}
    \caption{Sample task on Mechanical Turk}
    \label{fig:sample_task}
\end{figure}

The introduction listed Osborne's four rules of brainstorming \cite{osborn_applied_1957}, adapted to this context:

@@

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the risk their responses and idea generation processes evolved over time, making it difficult to compare their responses in the second HIT with responses from others who are performing the same HIT without any previous exposure to the problem. Accordingly, we retain only the first HIT submitted by each worker.

After removing these data, we are left with 146 distinct participants for a total of 146 HITs, yielding 3007 responses. A breakdown of responses across conditions is given in Table~\ref{tab:data_collected}.

\begin{table}[h!]
\begin{tabular}{r | l l l l l l l }
    & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline
    participants & 57 & 39 & 21 & 9 & 10 & 10 & 146 \\
    solutions & 283 & 372 & 413 & 450 & 635 & 855 & 3007
\end{tabular}
\caption{Data after removing unlimited condition and repeats}
\label{tab:data_collected}
\end{table}

@@

\subsubsection{Clustering: Terminology}
An \emph{instance} is a single solution by a single participant to a brainstorming question. Most concretely, it is the text entered into a single field in the web form. For example, four \emph{instances} from the data set:

\begin{enumerate}
    \item "Storage Container"
    \item "Small Storage Box"
    \item "Coin Storage"
    \item "Travel Jewelry Case"
\end{enumerate}

@@

In a category tree, ideas act as nodes. Each idea may optionally have a single parent idea, and zero or more child ideas. If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B. An example category tree for the instances above is given in Figure~\ref{fig:example_instances}.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{example_instances}
    \caption{Example category tree}
    \label{fig:example_instances}
\end{figure}
